---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statsapps

<!-- badges: start -->
<!-- badges: end -->

The statsapps package features interactive Shiny apps to help you learn 
concepts from data science & statistics. 

## Installation

You can install the development version of statsapps from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("vbaliga/statsapps")
```

## Example

Placeholder for example (TBD)

```{r example}
#library(statsapps)
## basic example code
```

# Contributing and/or raising Issues

Feedback on bugs, improvements, and/or feature requests are all welcome. Please see the Issues templates on GitHub to make a bug fix request or feature request.

To contribute code via a pull request, please consult the Contributing Guide first.


# Citation

TBD

# License

See LICENSE file (MIT)

🐢
